---
title: "Exploring Car Data with mtcars - Adv R Homework1"
author: "Kritheshvar - 24233014"
format: 
  pdf:
    toc: false
    number-sections: false
    code-block-border-left: true
    code-fold: false
    include-in-header: 
      text: |
        \usepackage{xcolor}
execute:
  echo: false  # hides the code
---

# **Introduction**

The `mtcars` dataset is a classic dataset in R that comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models). We will explore the relationship between **miles per gallon (mpg)** and **horsepower (hp)**.

# **Approach**

We will:
- Load the built-in `mtcars` dataset.
- Plot `mpg` against `hp`.
- Add a trend line for interpretation.
- Comment on the observed relationship.

# **Descriptive Statistics**

Here are some basic statistics of the key variables:

- **Mean mpg**: *`r mean(mtcars$mpg)`*
- **Mean hp**: *`r mean(mtcars$hp)`*
- **Max hp**: *`r max(mtcars$hp)`*
- **Min mpg**: *`r min(mtcars$mpg)`*

```{r}
library(ggplot2)
```

# **Plot**

Below is a scatter plot of `mpg` vs `hp`. We expect an inverse relationship: as horsepower increases, fuel efficiency (mpg) tends to decrease.

```{r}
ggplot(mtcars, aes(x = hp, y = mpg)) +
  geom_point(color = "steelblue", size = 2) +
  geom_smooth(method = "lm", se = FALSE, color = "darkred") +
  labs(title = "Miles per Gallon vs Horsepower",
       x = "Horsepower (hp)",
       y = "Miles per Gallon (mpg)") +
  theme_minimal()
```